The answer is that Alice wins. Let's define a Bob-set $V$ to be a set of points in the plane with no three collinear and with all distances at least $1$. The point of the problem is to prove the following fact.
Claim: Given a Bob-set $V \subseteq {\mathbb R}^2$, consider the Bob-graph with vertex set $V$ defined as follows: draw edge $ab$ if and only if the disk with diameter $\overline{ab}$ contains no other points of $V$ on or inside it. Then the Bob-graph is (i) connected, and (ii) planar.
Proving this claim shows that Alice wins since Alice can specify $\mathcal{S}$ to be the set of points outside the disk of diameter $PQ$.
Proof. [Proof that every Bob-graph is connected] Assume for contradiction the graph is disconnected. Let $p$ and $q$ be two points in different connected components. Since $pq$ is not an edge, there exists a third point $r$ inside the disk with diameter $\overline{pq}$.
Hence, $r$ is in a different connected component from at least one of $p$ or $q$ --- let's say point $p$. Then we repeat the same argument on the disk with diameter $\overline{pr}$ to find a new point $s$, non-adjacent to either $p$ or $r$. See the figure below, where the X'ed out dashed edges indicate points which are not only non-adjacent but in different connected components.

In this way we generate an infinite sequence of distances $\delta_1$, $\delta_2$, $\delta_3$, \dots\ among the non-edges in the picture above. By the ``Pythagorean theorem'' (or really the inequality for it), we have\[ \delta_i^2 \le \delta_{i-1}^2 - 1 \]and this eventually generates a contradiction for large $i$, since we get $0 \le \delta_i^2 \le \delta_1^2 - (i-1)$. $\blacksquare$
Proof. [Proof that every Bob-graph is planar] Assume for contradiction edges $ac$ and $bd$ meet, meaning $abcd$ is a convex quadrilateral. WLOG assume $\angle bad \ge 90^{\circ}$ (each quadrilateral has an angle at least $90^{\circ}$). Then the disk with diameter $\overline{bd}$ contains $a$, contradiction. $\blacksquare$